Checkpoint 4

### 2020-04-30 Checkpoint 4.Rmd
quinn does model eval

```{r}
Finaldata<-read_csv("time_series_final_Data.csv")
```

@@

#Quinn making models
```{r, cahce=TRUE}
set.seed(454)
Finaldata<-
  Finaldata%>%
  mutate(Day=as.numeric(Day))

model_1 <- stan_glmer(
  ChinaVirusInterest ~ (1 | State), #Gives us random intercepts
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)
```

```{r}
head(data.frame(summary(model_1)),-2)
```

#Quinn making models
```{r, warning=FALSE, cache=TRUE}
model_2 <- stan_glmer(
  ChinaVirusInterest ~ Day + (Day | State),
  data = Finaldata, family = gaussian,
  chains = 4, iter = 100, refresh = 0
)

@@

```{r}
head(data.frame(summary(model_2)),-2)
```

#Quinn makes models
```{r, warning = FALSE, cache=TRUE}
model_3 <- stan_glmer(
  ChinaVirusInterest ~ Day + StateColor + (Day | State),#Random intercepts and slopes when we put Day in
  data = Finaldata, family = gaussian,
  chains = 4, iter = 100, refresh = 0
)
```

```{r}
head(data.frame(summary(model_3)),-2)
```

#Quinn makes models
```{r, warning = FALSE, cache=TRUE}
model_4 <- stan_glmer(
  ChinaVirusInterest ~ Day + totalTestResults + (Day | State),#Random intercepts and slopes when we put Day in
  data = Finaldata, family = gaussian,
  chains = 4, iter = 100, refresh = 0
)
```

```{r}
head(data.frame(summary(model_4)),-2)
```

```{r, warning = FALSE, cache=TRUE}
model_5 <- stan_glmer(
  ChinaVirusInterest ~ Day + totalTestResults + positive + percent_white +  (Day | State),#Random intercepts and slopes when we put Day in
  data = Finaldata, family = gaussian,
  chains = 4, iter = 100, refresh = 0
)

@@

>>>>

```{r, warning=FALSE}
Finaldata<-read_csv("time_series_final_Data.csv")
```

@@

#Quinn making models
```{r, cahce=TRUE}
# 
# model_1 <- stan_glmer(
#   ChinaVirusInterest ~ (1 | State), #Gives us random intercepts
#   data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
# )
```

```{r}
# head(data.frame(summary(model_1)),-2)
```

#Quinn making models
```{r, warning=FALSE, cache=TRUE}
# model_2 <- stan_glmer(
#   ChinaVirusInterest ~ Day + (Day | State),
#   data = Finaldata, family = gaussian,
#   chains = 4, iter = 100, refresh = 0
# )

@@

```{r}
# head(data.frame(summary(model_2)),-2)
```

#Quinn makes models
```{r, warning = FALSE, cache=TRUE}
# model_3 <- stan_glmer(
#   ChinaVirusInterest ~ Day + StateColor + (Day | State),#Random intercepts and slopes when we put Day in
#   data = Finaldata, family = gaussian,
#   chains = 4, iter = 100, refresh = 0
# )
```

```{r}
# head(data.frame(summary(model_3)),-2)
```

#Quinn makes models
```{r, warning = FALSE, cache=TRUE}
# model_4 <- stan_glmer(
#   ChinaVirusInterest ~ Day + totalTestResults + (Day | State),#Random intercepts and slopes when we put Day in
#   data = Finaldata, family = gaussian,
#   chains = 4, iter = 100, refresh = 0
# )
```

```{r}
# head(data.frame(summary(model_4)),-2)
```

```{r, warning = FALSE, cache=TRUE}
model_100 <- stan_glmer(
  ChinaVirusInterest ~ Day + totalTestResults + positive + percent_white +  (Day | State),#Random intercepts and slopes when we put Day in
  data = Finaldata, family = gaussian,
  chains = 4, iter = 5000*2, refresh = 0
)

@@

```{r}
head(data.frame(summary(model_100)),-2)
```
```{r}
mcmc_trace(model_100)
mcmc_dens_overlay(model_100) #How can we just get a snapshot of our model evals?
```

```{r}
pp_check(model_100)
```

```{r}
set.seed(454)
pred_1 <- posterior_predict(
  model_100,
  newdata = Finaldata, transform = TRUE)

prediction_summary(y = Finaldata$ChinaVirusInterest,
  yrep = pred_1)
```

```{r}
### For predicting one case 
new_FL <- data.frame(Day = 7 , State = FL) #Doesn't recognize state

set.seed(454)
pred_FL <- posterior_predict(
  model_100,
  newdata = new_FL)

pred_100 <- data.frame(y_new = pred_100[-1])

ggplot(pred_100, aes(x=y_new))+geom_density()

summary(pred_100)

```{r}
# For correlation check (type like model 2 from activity 19)
# Store the chains
model_100_df <- as.array(model_100) %>%
  melt %>%
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
# Note the need for `...` around the sigma_sq_b
model_100_df <- model_100_df %>%
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
  mutate(correlation = (sigma_sq_b/(sigma_sq_w+sigma_sq_b)))

ggplot(model_100_df, aes(x = correlation)) +
  geom_density(alpha = 0.5)
```
